Species persistence under climate and fishing

### 2014-01-31 Writing/MS.tex
Edits out catch story, close #13

\noindent Second, we examined harvesting rules more complex than harvesting a constant proportion of the population. Whereas population persistence in the analytical model does not depend on the functional form of recruitment $f$, to perform simulations we must 
specify a recruitment function.  Again, we chose to use a Beverton-Holt function.  In the first generation, we seeded the world with 50 individuals at a single point, as in \citep{ZhouKot2011}. We first ran through 150 generations in order for the population to reach equilibrium without harvesting or climate shift.  We then added harvesting pressure, allowed the population to again reach equilibrium, and finally added climate change by moving the viable patch.  Equilibrium is calculated as the mean of 300 time steps once the difference in biomass between time step $t$ and $t+1$ was no greater than $0.1$.  Equilibrium biomass and catch are defined as the total amount of fish present and harvested, respectively, at equilibrium.

>>>>

\noindent Second, we examined harvesting rules more complex than harvesting a constant proportion of the population. Whereas population persistence in the analytical model does not depend on the functional form of recruitment $f$, to perform simulations we must 
specify a recruitment function.  Again, we chose to use a Beverton-Holt function.  In the first generation, we seeded the world with 50 individuals at a single point, as in \citep{ZhouKot2011}. We first ran through 150 generations in order for the population to reach equilibrium without harvesting or climate shift.  We then added harvesting pressure, allowed the population to again reach equilibrium, and finally added climate change by moving the viable patch.  Equilibrium biomass is calculated as the mean biomass of 300 time steps once the difference in biomass between time step $t$ and $t+1$ was no greater than $0.1$.
